%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Plasmati Graduate CV
% LaTeX Template
% Version 1.0 (24/3/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Alessandro Plasmati (alessandro.plasmati@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template needs to be compiled with XeLaTeX.
% The main document font is called Fontin and can be downloaded for free
% from here: http://www.exljbris.com/fontin.html
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[a4paper,10pt]{extarticle} % Default font size and paper size

\usepackage{fontspec} % For loading fonts
\defaultfontfeatures{Mapping=tex-text}
\setmainfont[SmallCapsFont = Fontin SmallCaps]{Fontin} % Main document font
\fontspec{[FontAwesome.otf]}


\usepackage{xunicode,xltxtra,url,parskip} % Formatting packages

\usepackage[usenames,dvipsnames]{xcolor} % Required for specifying custom colors

%\usepackage[big]{layaureo} % Margin formatting of the A4 page, an alternative to layaureo can be 
%\usepackage{fullpage}
\usepackage{geometry}
%\geometry{a4paper,margin=1.25cm}
\geometry{a4paper,total={175mm,257mm}}
 %To reduce the height of the top margin uncomment: \addtolength{\voffset}{-1.3cm}

\usepackage{hyperref} % Required for adding links	and customizing them
%\definecolor{linkcolour}{rgb}{0,0.2,0.6} % Link color
\definecolor{linkcolour}{rgb}{0.45,0.45,0.45} % Link color
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour} % Set link colors throughout the document

\usepackage{titlesec} % Used to customize the \section command
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule] % Text formatting of sections
\titlespacing{\section}{0pt}{0pt}{0pt} % Spacing around sections

\usepackage{multicol}
\setlength{\columnsep}{1cm}

\usepackage{textcomp}

\usepackage{fontawesome}

\begin{document}

\pagestyle{empty} % Removes page numbering

\font\fb=''[cmr10]'' % Change the font of the \LaTeX command under the skills section

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\par{\centering{\Huge R \textsc{Naresh}}\par} % Your name
\par{\centering\large {\textsc{Department of Computer Science and Engineering}}\par}\large
\par{\centering\large {\textsc{Undergraduate student at Indian Institute of Technology, Kharagpur}}\par}\large
\par{\centering\large {\textsc{A-209, LBS Hall of Residence, IIT Kharagpur, West Bengal - 721302}}\par}\large
\hspace{0.5cm}\normalsize \faEnvelope\ {\href{mailto:nareshmdu@gmail.com}{nareshmdu@gmail.com}}\hfill \normalsize  \faGlobe\ {\href{http://ghostwriternr.me/}{ghostwriternr.me}} \hfill \normalsize \faGithub\ {\href{https://github.com/ghostwriternr}{ghostwriternr}}\hfill \normalsize  \faLinkedinSquare\ {\href{https://www.linkedin.com/in/naresh-r-464a8b8b}{naresh-r}} \hfill {\faPhone\ +91-7872833729} \hspace{0.5cm} \\[10pt]

\textbf{\large{Company Recruitment Team}} \hfill \textit{August 9, 2016}

\textsc{SoundCloud} \\
\textsc{Rheinsberger straße 76/77 Berlin}\\
\textsc{Berlin 10115 Germany} \\

\underline{\textbf{Job Application for the role of Intern, Growth}}

Dear sir or madam,\\

Being someone who listens to brilliant music from Indie artists all the time, I only wonder how someone living in a very different corner of the world could connect with me. Thankfully, SoundCloud has just been the right platform helping millions of amazing artists get into the limelight. Instead of just passively appreciating the team that shares my same passion, I would love to work on such a remarkable platform and contribute as much as I can to this wonderful community. \\

I’ve completed one Engineering internship, and was offered a full-time position by the company's VP for my addicition to getting the work done. I am devoted to the field of Computer Science and have been exploring several fields over the last couple of years. Recently, I've narrowed down my research interests to Natural Language Processing (NLP), Image Processing (IP) and Machine Learning (ML). I am sufficiently proficient with several front-end and back-end technologies, and open to work on either end of the spectrum. I have expanded my rhetorical skills greatly over the past years thanks to a fair level of public speaking during my intership and my tenure as a governer at my college's literary society. \\

I am a conscientious person who believes in hard work and attention to detail. I thorougly enjoy working with a team, as it helps expand my thinking capabilities and ideas. I'm flexible and usually quick to pick up new skills. Thanks to the brilliant work culture currently instilled at SoundCloud, I believe I will be able to work at maximum efficiency and make more than satisfactory contributions to the project(s) allotted.\\

I look forward to speaking with you in further detail about the internship and opportunity with SoundCloud. I hope I’ll get the chance to show you more of my abilities once I join your team.\\

Sincerely,

\textbf{\large{R Naresh}}\\
Department of Computer Science and Engineering\\
Indian Institute of Technology, Kharagpur\\
West Bengal, India\\

\itshape{Attached: Curriculum Vitae}

\end{document}
